### 2013-09-26 evaluation/paper.tex
typo
try to refer to the rows in the plots in a less confusing way

Next, we consider the multi-label task.  The results for the \textsc{yeast} and \textsc{scene}
datasets are shown in \Figref{multi-label-results}. The caching $1$-slack
algorithm is much faster than the non-caching one on both datasets and both
graph structures.
While the two variants of the $n$-slack algorithm are equally fast with respect
to passes over the training data, solving the QP every 100 steps is among the
fastest algorithms, while solving the QP at every step is among the slowest.
We applied this method only to the smaller \textsc{scene} dataset, as applying it on the
\textsc{yeast} dataset was not practicable.

@@

The situation is very different when using the linear programming relaxation.
Looking at the four plots at the bottom of \Figref{snakes_results}, we see that all
algorithms are able to solve the task perfectly. Evaluating on the test-set, all algorithms
achieve an accuracy of around 99.5\%, confirming the models actually learned the task.
Surprisingly, SSGD was very successful on this dataset, even faster then the non-caching $n$-slack
algorithm. Caching provides nearly an order of magnitude speed-up on the dataset.
%
Using branch-and-bound to obtain exact results was not feasible on this dataset.

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_time_loss}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_time_loss}
    \end{tabu}
\caption{%
    Results on the \textsc{snakes} dataset. The top four plots show results using fusion
    move inference, the bottom four plots using AD$^3$. Dashed lines indicate the dual objective.
\figlabel{snakes_results}}
\end{figure}

The last set of experiments is on the segmentation dataset MSRC-21 and \textsc{Pascal
VOC}.  Because of the large number of labels and samples, it is only feasible
to use the fusion move inference algorithm. The results are shown in
\Figref{msrc_pascal_curves}, with the top four plots showing results on
MSRC-21, and the bottom four plots showing results on \textsc{Pascal VOC}.
First, we notice that all algorithms achieve low (approximate) duality gaps, and none
of the algorithms terminates prematurely. Also, all algorithms achieve a
similar dual objectives and similar training errors after convergence.
In both datasets, the $1$-slack algorithm is somewhat slow in minimizing the
training set error, and the $n$-slack and stochastic algorithms are much
faster. Solving the QP only every 100 steps in the $n$-slack algorithm significantly slows
down learning on both datasets. This is in contrast to the \textsc{yeast} datasets, where the converse was true,
even though \textsc{yeast} has a similar number of training examples to \textsc{Pascal VOC}.

@@

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/msrc}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/msrc_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time_loss}\\
    \includegraphics[width=\linewidth]{evaluation/images/pascal}&%
    \includegraphics[width=\linewidth]{evaluation/images/pascal_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/pascal_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/pascal_time_loss}
    \end{tabu}
\caption{%
    Objective and traning set loss on the segmentation task. The top four plots
    show results for the MSRC-21 dataset, the bottom four plots for the \textsc{Pascal
    VOC} dataset.
\figlabel{msrc_pascal_curves}}
\end{figure}

>>>>

Next, we consider the multi-label task.  The results for the \textsc{yeast} and \textsc{scene}
datasets are shown in \Figref{multi-label-results}. The caching $1$-slack
algorithm is much faster than the non-caching one on both datasets and both
graph structures.
While the two variants of the $n$-slack algorithm are equally fast with respect
to passes over the training data, solving the QP every 100 steps is among the
fastest algorithms, while solving the QP at every step is among the slowest.
We applied this method only to the smaller \textsc{scene} dataset, as applying it on the
\textsc{yeast} dataset was not practical.

@@

The situation is very different when using the linear programming relaxation.
Looking at last two rows of \Figref{snakes_results}, we see that all
algorithms are able to solve the task perfectly. Evaluating on the test-set, all algorithms
achieve an accuracy of around 99.5\%, confirming the models actually learned the task.
Surprisingly, SSGD was very successful on this dataset, even faster then the non-caching $n$-slack
algorithm. Caching provides nearly an order of magnitude speed-up on the dataset.
%
Using branch-and-bound to obtain exact results was not feasible on this dataset.

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_time_loss}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_time_loss}
    \end{tabu}
\caption{%
    Results on the \textsc{snakes} dataset. The first two rows show results using fusion
    move inference, the two rows below using AD$^3$. Dashed lines indicate the dual objective.
\figlabel{snakes_results}}
\end{figure}

The last set of experiments is on the segmentation dataset MSRC-21 and \textsc{Pascal
VOC}.  Because of the large number of labels and samples, it is only feasible
to use the fusion move inference algorithm. The results are shown in
\Figref{msrc_pascal_curves}, with the plots in the two upper rows showing results on
MSRC-21, and the tow rows below showing results on \textsc{Pascal VOC}.
First, we notice that all algorithms achieve low (approximate) duality gaps, and none
of the algorithms terminates prematurely. Also, all algorithms achieve a
similar dual objectives and similar training errors after convergence.
In both datasets, the $1$-slack algorithm is somewhat slow in minimizing the
training set error, and the $n$-slack and stochastic algorithms are much
faster. Solving the QP only every 100 steps in the $n$-slack algorithm significantly slows
down learning on both datasets. This is in contrast to the \textsc{yeast} datasets, where the converse was true,
even though \textsc{yeast} has a similar number of training examples to \textsc{Pascal VOC}.

@@

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/msrc}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/msrc_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time_loss}\\
    \includegraphics[width=\linewidth]{evaluation/images/pascal}&%
    \includegraphics[width=\linewidth]{evaluation/images/pascal_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/pascal_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/pascal_time_loss}
    \end{tabu}
\caption{%
    Objective and traning set loss on the segmentation task. The first two rows
    show results for the MSRC-21 dataset, the rows below for the \textsc{Pascal
    VOC} dataset.
\figlabel{msrc_pascal_curves}}
\end{figure}
